Keystoneness, centrality, and the structural controllability of ecological networks

### 2019-01-13 paper/supp-info.Rmd
caught a few minor typos in the supps

All of these non-reciprocal networks are as likely to be one that best represents the superior/matched relationships in the network. 
As such, we average the three metrics ($n_D$, $\phi$, and $\sigma$) across all the networks without reciprocal links without weighting by the number of possible control configurations. 
It is important to note that a species that is found to be a superior node under a particular control configuration, will be so in all possible control configurations for the particular non-reciprocal network. 
We, therefore denote the average of $\sigma$ across all non-reciprocal versions as the probability of the species being a superior node in its community.

@@

c_mod_table %>% 
  dplyr::mutate(weight = round(weight, 2)) %>%
  knitr::kable("latex", 
               escape = FALSE, 
               booktabs = TRUE, 
               digits = 2, 
               linesep = c(""),
               caption = "Model selection table based on the Akaike Information Criterion for small samples for candidate models of size of the minimum driver node set ($n_D$) in the empirical networks. The evaluated variables are: the invasion status (inv), the network connectance ($C$), the network nestedness (NODF) the number of species ($n_S$) the network asymmetry ($AS_s$) or the interaction strength asymmetry ($AS_s$). Only candidate models with a weight $>0.01$ are shown.") %>%
  kableExtra::kable_styling(font_size = 8)
```

>>>>

All of these non-reciprocal networks are as likely to be one that best represents the superior/matched relationships in the network. 
As such, we average the three metrics ($n_D$, $\phi$, and $\sigma$) across all the networks without reciprocal links without weighting by the number of possible control configurations. 
It is important to note that a species that is found to be a superior node under a particular control configuration will be so in all possible control configurations for the particular non-reciprocal network. 
We therefore denote the average of $\sigma$ across all non-reciprocal versions as the probability of the species being a superior node in its community.

@@

c_mod_table %>% 
  dplyr::mutate(weight = round(weight, 2)) %>%
  knitr::kable("latex", 
               escape = FALSE, 
               booktabs = TRUE, 
               digits = 2, 
               linesep = c(""),
               caption = "Model selection table based on the Akaike Information Criterion for small samples for candidate models of size of the minimum driver node set ($n_D$) in the empirical networks. The evaluated variables are: the invasion status (inv), the network connectance ($C$), the network nestedness (NODF) the number of species ($n_S$) the network asymmetry ($AS_n$) or the interaction strength asymmetry ($AS_s$). Only candidate models with a weight $>0.01$ are shown.") %>%
  kableExtra::kable_styling(font_size = 8)
```
